Predicting Diabetes Based on Various Factors Using Decision Tree Analysis

### 2023-12-15 manuscript/manuscript.tex
Minor edits to formatting

After completing our methods section, we can now move on to talk about the results of our model. Based on Figure~ref{fig:importance}, we can 
see that the top three predictors are glucose, BMI, and age. The result of glucose being of the greatest importance makes complete sense with 
medical knowledge of diabetes as a patient that has high amounts of glucose in their bloodstream could have type 2 diabetes. This is known due
to glucose not being absorbed by insulin as these patients do not use insulin properly. We can see that almost all of the outcomes are explained
by glucose. The next predictor that is successful in predicting a large amount of the data is the patient's BMI. This aligns on a medical standpoint
as patients who have larger BMI values are more susceptable to getting type 2 diabetes as they are considered to be obese. Based on my results, BMI
was able to predict about half of the outcomes. The last predictor that proved to be valuable in predicting if someone has diabetes is age. This result
is somewhat medically backed but not entirely a result that I expected. Often times people that are older have diabetes due to numerous factors but it is 
not as common for younger patients.

@@

Looking at Table~ref{tab:dtr}, we can see that the accuracy of our model is 0.82, which is high so it will be satisfactory. This tells me that we 
classify correctly 82 percent of the time out of the total instances. The next metric we will look at is precision. We were able to get to 72 percent.
This is the ratio of correctly predicted positive observations to the total predicted positives. Looking at recall, we were able to correctly identify about
74 percent of the actual positive instances. This is pretty strong and will be considered satisfactory. The final metric that we have is the F1 score, which is the
harmonic mean of precision and recall, which we were able to get a value of 0.73. This indicates a balanced performance.

>>>>

After completing our methods section, we can now move on to talk about the results of our model. Based on Figure~\ref{fig:importance}, we can 
see that the top three predictors are glucose, BMI, and age. The result of glucose being of the greatest importance makes complete sense with 
medical knowledge of diabetes as a patient that has high amounts of glucose in their bloodstream could have type 2 diabetes. This is known due
to glucose not being absorbed by insulin as these patients do not use insulin properly. We can see that almost all of the outcomes are explained
by glucose. The next predictor that is successful in predicting a large amount of the data is the patient's BMI. This aligns on a medical standpoint
as patients who have larger BMI values are more susceptable to getting type 2 diabetes as they are considered to be obese. Based on my results, BMI
was able to predict about half of the outcomes. The last predictor that proved to be valuable in predicting if someone has diabetes is age. This result
is somewhat medically backed but not entirely a result that I expected. Often times people that are older have diabetes due to numerous factors but it is 
not as common for younger patients.

@@

Looking at Table~\ref{tab:dtr}, we can see that the accuracy of our model is 0.82, which is high so it will be satisfactory. This tells me that we 
classify correctly 82 percent of the time out of the total instances. The next metric we will look at is precision. We were able to get to 72 percent.
This is the ratio of correctly predicted positive observations to the total predicted positives. Looking at recall, we were able to correctly identify about
74 percent of the actual positive instances. This is pretty strong and will be considered satisfactory. The final metric that we have is the F1 score, which is the
harmonic mean of precision and recall, which we were able to get a value of 0.73. This indicates a balanced performance.
